ZCB Pricing

### 2018-06-25 ZCB Pricing .Rmd
Real Work
Addition of explicit method

---
title: "ZCB Pricing"
author: 
- Valentine Chisango
- George Parekkadavil
- Vegan Pather

date: "6/22/2018"
output: html_document
---

@@

```{r 3}
# Explicit Method
```

```{r 4}
# Implicit Method
```

```{r 5}
# Crank-Nicholson Method
```

```{r 6}
# Modified Fully Implicit Method
```

```{r 7, echo = FALSE}
# Comparison of results
# Varying short rates

>>>>

---
title: "ZCB Pricing"
author:
- Valentine Chisango
- George Parekkadavil
- Vegan Pather
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document: default
---

@@

```{r 3}
# Improvements to the Monte Carlo Simulation
# Antithetic Variates

```{r 4}
# Explicit Method

# Simple Bond price function
B <- function(t,r){
  exp(-(T-t)*r)
}

explicit <- function(alpha, beta, sigma, T, r, j, s){

# j = number of sub-intervals for the short rate
# s = number of sub-intervals for the time interval

dr = 1/j # lenght of short rate intervals
dt = T/s # lenght of time intervals

p_d <- sigma^2/(2*((dr)^2)) -(alpha -beta*r)/(2*dr)
p_m <- 1/dt -(sigma^2)/(dr^2)
p_u <- sigma^2/(2*(dr^2)) +(alpha -beta*r)/(2*dr)

V <- matrix(NA, nrow = j + 1, ncol = s + 1)
V[,s+1] <- rep(1)
V[j+1,] <- rep(1)
for (n in seq(s,0,-1)){
    for (i in 1:j)
       if (i == 1)
         V[i,n] <- ((0.10 +1/dt)^(-1))*(p_d*V[i+1,n+1] +p_m*V[i,n+1] + p_u*V[i+2,n+1]) #Vetzal approx
       else
         V[i,n] <- ((0.11 -0.01*i +1/dt)^(-1))*(p_d*V[i+1,n+1] +p_m*V[i,n+1] + p_u*V[i-1,n+1])

}
V
}

```{r 5}
# Implicit Method
```

```{r 6}
# Crank-Nicholson Method
```

```{r 7}
# Modified Fully Implicit Method
```

```{r 8, echo = FALSE}
# Comparison of results
# Varying short rates
